---
title: "Project 3: stat302package Tutorial"
author: "Edward Sung"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{stat302package Tutorial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(stat302package)
```

# Introductory

The PROJECT3 package is a final project for STAT 302. It can be used for a variety of uses including linear modeling, k-nearest-neighbors, t-tests, and Random Forest Cross Validation. To install the package from github, run the following code.


## Install Package from Github
```{r, eval=FALSE}
setwd("..")
devtools::install("stat302package")
library(YOUR_PACKAGE_NAME)
?my_pow

devtools::install_github("edwardsung63/stat302package")
library(stat302package)
?my_pow

library(stat302package)
```

# Tutorial for my_t_test()

All the tests demonstrated below use `lifeExp` data from `my_gapminder`.
# case I: alternative = "two.sided"
  \begin{align}
  H_0: \mu &= 60,\\
  H_a: \mu &\neq 60.
  \end{align}
```{r}
data("my_gapminder")
my_t_test(my_gapminder$lifeExp, alternative = "two.sided", mu = 60)
```
From the test result, we notice that the p_value is greater than 0.05. Thus, it is not statistically significant have no enough evidence to reject the null hypothesis.

# case II: alternative = "less"
  \begin{align}
  H_0: \mu &= 60,\\
  H_a: \mu &< 60.
  \end{align}
```{r}
my_t_test(my_gapminder$lifeExp, alternative = "less", mu = 60)
```
From the test result, we notice that the p_value is less than 0.05. Thus, it is not statistically significant have no enough evidence to reject the null hypothesis.

# case III: alternative = "greater"
  \begin{align}
  H_0: \mu &= 60,\\
  H_a: \mu &> 60.
  \end{align}
```{r}
my_t_test(my_gapminder$lifeExp, alternative = "greater", mu = 60)
```
From the test result, we notice that the p_value is greater than 0.05. Thus, it is not statistically significant have no enough evidence to reject the null hypothesis.


# Tutorial for my_lm()
```{r, eval=FALSE}
test <- my_lm(my_fml = lifeExp ~ gdpPercap + continent, my_data = my_gapminder)
my_coef <- test[1]
my_matrix <- cbind(1, my_gapminder$gdpPercap)
y_hat <- my_matrix %*% as.matrix(my_coef)
plot(my_gapminder$lifeExp, y_hat)
expect_is(my_lm(pop ~ gdpPercap, my_data = my_gapminder), "table")
```
As shown, we notice that the difference of `lifeExp` between two observations is an unit in `gdpPercap`. Compared to the coeffiecients of different continents, `gdpPercap` has less influence on `lifeExp` than `continent`.

# Tutorial for my_knn_cv()
```{r, eval=FALSE}
tutor_knn <- my_knn_cv(train = my_gapminder[, 3 : 4], 
                       cl = my_gapminder$continent, k_nn = 10, k_cv = 5)
```

# Tutorial for my_rf_cv()
```{r, eval=FALSE}
library(class)
library(tidyverse)
library(randomForest)
my_rf_cv <- function(k) {
  fold <- sample(rep(1:k, length = length(my_gapminder$lifeExp)))
  # data <- data.frame()
  mse <- rep(NA, k)
  # loop thru the folds
  for (i in 1:k) {
    data_train <- iris[fold != i, ] # Xi
    data_test <-  iris[fold == i, ]  # Xi star
    # Train our models
    cl_train <- my_gapminder$lifeExp[fold != i] # Yi
    cl_test <- my_gapminder$lifeExp[fold == i]  # Yi star
    model <- randomForest(lifeExp ~ gdpPercap, data = data_train, ntree = 100)
    predictions <- predict(model, data_test[, -1])
    mse[i] <- mean((predictions - cl_test)^2)
  }
  output <- mean(mse)
}

# ########################
k_vector <- c(2, 5, 10, 100)
tutor_rf <- matrix(NA, nrow = 30, ncol = 4)
for (i in 1 : length(k_vector)) {
  for (k in 1 : 30) {
    tutor_rf[k, i] <- my_rf_cv(k = k_vector[i])
  }
}
tutor_rf
```
